Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-10-23 doc/Paper/main.tex
Acknowledgments.

    We anticipate that these results will be useful for forecasting the constraining power of magnitude-limited samples, e.g. from LSST. In the lower right panel of Fig.~\ref{fig:magnitude-cuts-bias}, we show a comparison between the biases derived using our fitting function to those assumed in the DESC Science Requirements Document (SRD) analysis. As can be seen, we find significant differences between these two. An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula. Our parameter chains for halo model and systematics parameters for the different limiting magnitudes are available upon request. 
    %Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%. The same data could also be used to compare the effective number densities. In fact \cite{1809.01669} already uses the HSC-SSP data to estimate number densities. We do find, however, that compared to LSST DESC SRD, the area lost to masking is considerably higher, around 20\% rather than 12\% assumed in \cite{1809.01669}.
    \begin{figure}
      \begin{center}
        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
          \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_i24p5-vs-DESC-SRD.pdf}} 
        \caption{\textit{Upper panels:} Constraints on the large-scale galaxy bias $b(z)$ and $b(z)D(z)$ as a function of redshift for the different magnitude-limited galaxy samples considered in this analysis. For all plots, the points denote the values derived from the mean of the posterior distribution of the parameters and the solid lines show the predictions from the fitting function given in Equations \ref{eq:bias-fit-func} and \ref{eq:bias-fit-func-result}. The shaded regions denote the $68 \%$ c.l.. \textit{Lower left panel:} Constraints on $\bar{b}(m_{\mathrm{lim}})$, as defined in Eq.~\ref{eq:bias-fit-func}. The solid line illustrates the best-fit relation given in Eq.~\ref{eq:bias-fit-func-result}. \textit{Lower right panel:} Comparison of the results obtained in this analysis to the bias values assumed for LSST forecasts in the DESC SRD.}
        \label{fig:magnitude-cuts-bias}
      \end{center}
    \end{figure}

@@

\acknowledgments
  DA acknowledges support from the Beecroft trust and from the Science and Technology Facilities Council through an Ernest Rutherford Fellowship, grant reference ST/P004474/1.
  HA, BA and EG have been supported by the Rutgers Discovery Informatics Institute Fellowship of Excellence in Computational and Data Science (AY 2017-2020) and Rutgers University \& Bevier Dissertation Completion Fellowship (AY 2019-2020).
  HA, AB, and EG were supported by the Department of Energy (grants DE-SC0011636 and DE-SC0010008).
  HA also thanks the LSSTC Data Science Fellowship Program, which is funded by LSSTC, NSF Cybertraining Grant \#1829740, the Brinson Foundation, and the Moore Foundation, as participation in the program has benefited this work.
  ZG is supported by a Rhodes Scholarship granted by the Rhodes Trust.
  RM is supported by the Department of Energy Cosmic Frontier program, grant DE-SC0010118.
  HM has been supported by the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration and Grant-in-Aid for Scientific Research from the JSPS Promotion of Science (No. 18H04350). 
  JAN us supported by grant DOE DE-SC0007914 from the U.S. Department of Energy Office of Science (Office of High Energy Physics).
  This manuscript has been authored by Fermi Research Alliance, LLC under Contract No. DE-AC02-07CH11359 with the U.S. Department of Energy, Office of Science, Office of High Energy Physics.
  The work by JS was supported by the U.S. Department of Energy award DE-SC0009920.
  This work was supported by the grant MDM-2015-0509 from the Spanish Ministry of Science and Innovation.
  This project was supported in part by the U.S. Department of Energy, Office of Science, Office of Workforce Development for Teachers and Scientists (WDTS) under the Science Undergraduate Laboratory Internships Program (SULI).

>>>>

    We anticipate that these results will be useful for forecasting the constraining power of magnitude-limited samples, e.g. from LSST. In the lower right panel of Fig.~\ref{fig:magnitude-cuts-bias}, we show a comparison between the biases derived using our fitting function to those assumed in the DESC Science Requirements Document (SRD) analysis. As can be seen, we find these two to differ at approximately $2 \sigma$, using the uncertainties on our bias measurement. An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula. Our parameter chains for halo model and systematics parameters for the different limiting magnitudes are available upon request. 
    %Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%. The same data could also be used to compare the effective number densities. In fact \cite{1809.01669} already uses the HSC-SSP data to estimate number densities. We do find, however, that compared to LSST DESC SRD, the area lost to masking is considerably higher, around 20\% rather than 12\% assumed in \cite{1809.01669}.
    \begin{figure}
      \begin{center}
        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}} 
          \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_i24p5-vs-DESC-SRD.pdf}} 
        \caption{\textit{Upper panels:} Constraints on the large-scale galaxy bias $b(z)$ and $b(z)D(z)$ as a function of redshift for the different magnitude-limited galaxy samples considered in this analysis. For all plots, the points denote the values derived from the mean of the posterior distribution of the parameters and the solid lines show the predictions from the fitting function given in Equations \ref{eq:bias-fit-func} and \ref{eq:bias-fit-func-result}. The shaded regions denote the $68 \%$ c.l.. \textit{Lower left panel:} Constraints on $\bar{b}(m_{\mathrm{lim}})$, as defined in Eq.~\ref{eq:bias-fit-func}. The solid line illustrates the best-fit relation given in Eq.~\ref{eq:bias-fit-func-result}. \textit{Lower right panel:} Comparison of the results obtained in this analysis to the bias values assumed for LSST forecasts in the DESC SRD.}
        \label{fig:magnitude-cuts-bias}
      \end{center}
    \end{figure}

@@

\acknowledgments
  DA acknowledges support from the Beecroft trust and from the Science and Technology Facilities Council through an Ernest Rutherford Fellowship, grant reference ST/P004474/1.
  AN would like to thank Jo Dunkley and David Spergel for numerous helpful discussions and suggestions. AN further acknowledges support from National Science Foundation Grant No. 1814971.
  HA, BA and EG have been supported by the Rutgers Discovery Informatics Institute Fellowship of Excellence in Computational and Data Science (AY 2017-2020) and Rutgers University \& Bevier Dissertation Completion Fellowship (AY 2019-2020).
  HA, AB, and EG were supported by the Department of Energy (grants DE-SC0011636 and DE-SC0010008).
  HA also thanks the LSSTC Data Science Fellowship Program, which is funded by LSSTC, NSF Cybertraining Grant \#1829740, the Brinson Foundation, and the Moore Foundation, as participation in the program has benefited this work.
  ZG is supported by a Rhodes Scholarship granted by the Rhodes Trust.
  RM is supported by the Department of Energy Cosmic Frontier program, grant DE-SC0010118.
  HM has been supported by the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration and Grant-in-Aid for Scientific Research from the JSPS Promotion of Science (No. 18H04350). 
  JAN us supported by grant DOE DE-SC0007914 from the U.S. Department of Energy Office of Science (Office of High Energy Physics).
  This manuscript has been authored by Fermi Research Alliance, LLC under Contract No. DE-AC02-07CH11359 with the U.S. Department of Energy, Office of Science, Office of High Energy Physics.
  The work by JS was supported by the U.S. Department of Energy award DE-SC0009920.
  This work was supported by the grant MDM-2015-0509 from the Spanish Ministry of Science and Innovation.
  This project was supported in part by the U.S. Department of Energy, Office of Science, Office of Workforce Development for Teachers and Scientists (WDTS) under the Science Undergraduate Laboratory Internships Program (SULI).
